Speeding up eQTL scans in the BXD population using GPU

### 2019-10-08 paper.tex
added a paragraph for Why GPU in introduction.

%Why GPU?
Processing large data set has been a challenge for genome scan. 
We were blessed with Moore's Law for decades, but the Central Processing Unit (CPU) is reaching to its physical limit of transistors. 
Graphics Processing Unit (GPU), originally used as an image processing component of a computer, has shown some compelling results of accelerating computation in various fields.
General Purpose computing Graphics Processor (GPGPU) became popular in the early 2000s because of its ability to natively handel matrix and vector operations. 
Such power is very attractive to the scientific computing community. 
BXD genome scan can be simplified down to matrix operations, which is quite amendable to GPU computing.

@@

The matrix multiplication with large matrices is the most computationally intensive and time-consuming 
to perform eQTL analysis.  By dividing large matrices into small block matrices, 
one can achieve striking efficiency in matrix multiplication in conjunction with built-in BLAS in R, 
Intel Kernel Math Library (KML) in Revolution R/Matlab, or even GPU CUDA in Matlab.  
For instance, GOTO BLAS, only available in 64 bit R only, and KML allow the use of multiple CPU cores and provide 14-17 times 
better performance than built-in BLAS in R.  GPU-based computation shows 10 times better performance than 
the best algorithm for the CPU for single precision even if Matlab provides GPU CUDA but limited support to it  \citep{shabalin2012matrix}.

>>>>

@@

The matrix multiplication with large matrices is the most computationally intensive and time-consuming 
to perform eQTL analysis.  By dividing large matrices into small block matrices, 
one can achieve striking efficiency in matrix multiplication in conjunction with built-in BLAS in R, 
Intel Kernel Math Library (KML) in Revolution R/Matlab, or even in Matlab using CUDA.  
%For instance, GOTO BLAS, only available in 64 bit R only, and KML allow the use of multiple CPU cores and provide 14-17 times 
%better performance than built-in BLAS in R.  GPU-based computation shows 10 times better performance than 
%the best algorithm for the CPU for single precision even if Matlab provides GPU CUDA but limited support to it  \citep{shabalin2012matrix}.

%Why GPU?
Processing large data set has been a challenge for genome scan. 
We were blessed with Moore's Law for decades, but the Central Processing Unit (CPU) is reaching to its physical limit of transistors. 
Graphics Processing Unit (GPU), originally used as an image processing component of a computer, has shown some compelling results of accelerating computation in various fields.
General Purpose computing Graphics Processor (GPGPU) became popular in the early 2000s because of its ability to natively handel matrix and vector operations. 
Such power is very attractive to the scientific computing community. 
Zhang et al. \citep{zhang2015mixed} used GPU to simultaneously dissect various genetic effects with mixed linear model.

%previsou work on GPU
